---
title: "BeerCaseStudy"
author: "Will Holt and Yejur Kunwar"
date: "October 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro: Prior to working with the data Last Call Consluting (LCC) had to clean the respective data sets.
Changing column names to make them human readable and to also allow for an efficient merge

load the data
```{r}
Beer <- read.csv("Beers.csv")
Breweries <- read.csv("Breweries.csv")
```


```{r}
names(Beer) <- c("BeerName", "BeerID", "ABV", "IBU", "BreweryID", "BeerStyle", "Ounces")
str(Beer)
```

```{r}
names(Breweries) <- c("BreweryID", "BreweryName", "BreweryCity", "BreweryState")
str(Breweries)
```



###1. How many breweries are present in each state?
```{r}
StateBreweries <- as.data.frame(table(Breweries$BreweryState))
names(StateBreweries) <- c("BreweryState", "BreweryCount")
StateBreweries
```


###2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

```{r}
BeerStudy <- merge(Beer,Breweries,by="BreweryID")
head(BeerStudy, 6)
tail(BeerStudy, 6)
```


### 3. Report the number of NA's in each column.

```{r}
colSums(is.na(BeerStudy))
```

### 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

#### Complete plot
```{r}
ABVMedian <- aggregate(BeerStudy$ABV ~ BeerStudy$BreweryState, data = BeerStudy, median)
IBUMedian <- aggregate(BeerStudy$IBU ~ BeerStudy$BreweryState, data = BeerStudy, median)
ABV_IBU_Medians <- merge(ABVMedian, IBUMedian, by = "BeerStudy$BreweryState", all = TRUE)
```


### 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?
## clean the column names
```{r}
ABVMax <- aggregate(BeerStudy$ABV ~ BeerStudy$BreweryState, data = BeerStudy, max)
#code for max MaxABV_State <- all[order(-ABVMax$BeerStudy$ABV),]

```

### 6. Summary statistics for the ABV variable.
7. Is there an apparent relationship between the bitterness of the
beer and its alcoholic content? Draw a scatter plot.