---
Title: "Beer Case Study"
Author: "Will Holt and Yejur Kunwar"
Date: "October 17, 2017"
Output: html_document
---
![alt text][logo]
# Beer Case Study
[logo]: http://www.reyesbeveragegroup.com/Global/Logos/RBG-wheat-shield.png

### Background:
Reyes Beverage Group (Reyes), one of the largest beer distributor in the United States, is looking to brew its own beer in an effort to expand its own business. Specifically, Reyes is looking to produce seasonal beers with an alcohol by volume (ABV) content between 0.05 and 0.07. Reyes contacted Last Call Consulting (LCC) to determine states that are potential markets. 


### Scope:
LCC cleaned, and analyzed a list of beers and breweries by state from Open Beer DB (https://openbeerdb.com/). The analysis identified the top three states Reyes should target for its seasonal beers.


### Key Findings:
LCC determined that more than 75% of the beers were greater than or equal to 0.05 and that 25% of beers were greater than or equal to 0.067. This suggests that Reyes is producing a beer with an ABV that is not unsual for the market.
LCC identified Connecticut (CT), Maryland (MD), and Illinois (IL) as the three markets to target for their initial line of seasonal beers. CT, MD, and IL currently have eight, seven and 18 breweries respectively and a median ABV of 0.06 for CT, 0.058 for MD, and 0.058 for IL. CT's relative proiximity to New York City (NYC) may be advantageous as word of the new beer may spread amongst individuals who commute from CT to NYC. MD's close proximity to Washington D.C. (DC) could help Reyes gain entry to the DC market, which only has one brewery. IL allows Reyes to save money on shipping costs as it is located in Chicago and can leverage its relationships with Chicago business to help launch its product. As the product grows, Minnesota (MN) could be another midwestern market for Reyes to targt as it has 12 breweries and a median ABV of 0.056.

### Deliverables:
LCC provided an RMarkdown file, which included the associated codes so that Reyes can reproduce the research conducted and follow-up with any questions as needed. 
In addition, LCC produced a codebook and ReadMe file to ensure alignment and proper understanding of the variables and findings.
Within the RMarkedown file are key questions posed by Reyes CIO, Faizan Javed. 
```{r}
Beer <- read.csv("Beers.csv")
Breweries <- read.csv("Breweries.csv")
```


```{r}
names(Beer) <- c("BeerName", "BeerID", "ABV", "IBU", "BreweryID", "BeerStyle", "Ounces")
str(Beer)
```

```{r}
names(Breweries) <- c("BreweryID", "BreweryName", "BreweryCity", "BreweryState")
str(Breweries)
```



###1. How many breweries are present in each state?
There were instances in which a brewery appeared more than once in a state but was counted twice to show how breweries are successful in multiple cities throughout a state and to truly represent the number of breweries per state.
Should the CIO, Faizan Javed need to understand the unique count based on name only, LCC will provide updated findings.
```{r}
#A unique brewery is defined as a Brewery appearing in a different city (e.g. Victory Brewing, Kennett; Victory Brewing, Downingtown)
StateBreweries <- as.data.frame(table(Breweries$BreweryState))
names(StateBreweries) <- c("BreweryState", "BreweryCount")
StateBreweries
```


###2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

```{r}
BeerStudy <- merge(Beer,Breweries,by="BreweryID")
head(BeerStudy, 6)
tail(BeerStudy, 6)
```


### 3. Report the number of NA's in each column.

```{r}
colSums(is.na(BeerStudy))
```

### 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

```{r}
library(ggplot2)
#First set of code represents ABV Median by State
ABVMedian <- aggregate(BeerStudy$ABV ~ BeerStudy$BreweryState, data = BeerStudy, median)
names(ABVMedian) <- c("State", "ABV")
ABVMedian <- ABVMedian[order(ABVMedian$ABV,decreasing = TRUE),]
ggplot(data = ABVMedian, aes(x=reorder(ABVMedian$State, -ABVMedian$ABV), y=ABVMedian$ABV)) +
geom_bar(stat = "identity") +
labs(title = "ABV Median by State", x = "State", y = "Median")
#Second set of code represents IBU Median by State
IBUMedian <- aggregate(BeerStudy$IBU ~ BeerStudy$BreweryState, data = BeerStudy, median)
names(IBUMedian) <- c("State", "IBU")
IBUMedian <- IBUMedian[order(IBUMedian$IBU,decreasing = TRUE),]
ggplot(data = IBUMedian, aes(x=reorder(IBUMedian$State, -IBUMedian$IBU), y=IBUMedian$IBU)) +
geom_bar(stat = "identity") +
labs(title = "IBU Median by State", x = "State", y = "Median")
```


### 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

```{r}
#First code identifies the state with the highest ABV
head(ABVMedian, 1)
#Second code identifies the state with the highest IBU
head(IBUMedian, 1)
```

### 6. Summary statistics for the ABV variable.

```{r}
summary(BeerStudy$ABV)
```

### 7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.
Based on the visuals produced from the following code and an r-value of 0.6706215 we can see there is a moderate correlation between ABV and IBU in this particular dataset.

```{r}
ggplot(BeerStudy, aes(x=BeerStudy$ABV, y=BeerStudy$IBU)) + 
geom_point(size=2, shape=23) + 
labs(title = "Correlation of ABV and IBU", x = "ABV", y = "IBU")
#The following code will calcuate the r value and represents the coorelation between ABV and IBU
cor.test(BeerStudy$ABV, BeerStudy$IBU)
```


* Link for github: https://github.com/WillHolt-SMU/Beer-Case-Study
